LaTeX draft for \\"Ancient Greece Yuri Visual Novel"

### 2015-09-28 text/draft.tex
First draft of the "friends" ending

I sigh. lengthily.\\

@@

>>>>

I sigh. Lengthily.\\

@@

\gsection{Friends}

A hard silence sets between us for a moment. We're both reflecting on our own mistakes I guess. Finally, I risk a few words.\\

\speaker{Ambrosia} "Is there anything else you need to tell me?"\\

She hesitates, then shakes her head.

\speaker{Antiope} "I have a lot more depressing stories in reserve, but that's far enough for one night. Ambrosia... Thanks. For listening to me. For not having freaked out when I acted like that."\\

\speaker{Ambrosia} "Don't worry. That's what friends are for."\\

\speaker{Antiope} "Still. Thanks."\\

Antiope smiles, and my heart races. I feel like a liar. I probably am, if only by omission. Yet, this may be for the best. She doesn't need a psychotic lover right now. Just an attentive, friendly ear. Or so do I try to convince myself.\\

The rest of the night is actually rather pleasant. We chitchat. I manage to bring her to one of the last musical representations. I myself sing. We go to bed relaxed and relieved.\\

On the next morning, we depart, as we planned to. Our adventure continues the same, except Antiope is a little more talkative and open. A good end probably.\\

And yet, dark at night, when alone with my thoughts, a sombre part of me still burns with jealousy, desire and regret, wondering what could have happened had I taken my chance at that time.\\

\dcomment{
	An acid pseudo good end does not sound bad, but I think there is still work to do to flesh it out properly
}
